A Transactional Memory System for Parallel Python

### 2014-06-16 talk/dls2014/paper/paper.tex
fix some references

\authorinfo{Remigius Meier}
           {Department of Computer Science\\ ETH Zürich}
           {remi.meier@inf.ethz.ch}
\authorinfo{Armin Rigo}
           {www.pypy.org}
           {arigo@tunes.org}
\authorinfo{Thomas Gross}
           {Department of Computer Science\\ ETH Zürich}
           {thomas.gross@inf.ethz.ch}

>>>>

\authorinfo{Remigius Meier}
           {Department of Computer Science\\ ETH Zürich, Switzerland}
           {remi.meier@inf.ethz.ch}
\authorinfo{Armin Rigo}
           {www.pypy.org}
           {arigo@tunes.org}
\authorinfo{Thomas Gross}
           {Department of Computer Science\\ ETH Zürich, Switzerland}
           {thomas.gross@inf.ethz.ch}
